\begin{preface}
% CROWN JEWEL, BUSY AS A BEAVER, BLOOD SWEAT AND TEARS, RECHARGE ONE'S BATTERIES, ELVIS HAS LEFT THE BUILDING, FAT LADY SINGING
In front of you lies the thesis: "Efficient and Evasive Distributed Adversarial Attacks using Particle Swarm Optimization". The text is the result of a year of hard work and I am very proud of the final result.\\

The subject seemed very interesting when I first read about it in May of 2021. Having worked on it for the past year, I can guarantee you that it did not only seem an interesting topic, it proved to be one as well. I hope you agree with me once you have read this text and I wish you a lot of enjoyment in reading it.\\
 
This work will be the crown jewel of my academic career. After five years of blood, sweat and tears, albeit not literally, I can hear the fat lady singing in the distance. Before it is completely over, I want to thank everyone that helped me over the course of these five years. I want to thank my family and girlfriend for supporting me on this journey and proofreading all reports I have written, even though the contents of some of them was very difficult to grasp. I want to thank my friends for the fun times and the company during the lessons, some of which seemed to last for days. I want to thank the assessors and members of the jury for taking their time to read this text and triggering my brain one last time with their interesting remarks and questions. Last but not least, I want to thank my supervisor, co-supervisor and assistant-supervisors for the guidance throughout the year and their feedback on my intermediate work.\\

Elvis has left the building!\\
\end{preface}